---
title: "PAD_BAMDATA"
author: "Merritt Harlan"
date: "2/24/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Functions

```{r Functions}
library(bamr)

### Functions --------

#Calculate dA
#Calculate area
#' Calculate partial cross-section area from DAWG-formatted width and height matrices
#' @param w Matrix of widths
#' @param h Matrix of heights(FROM MARK)
calcdA_mat <- function(w, h) {
  stopifnot(all(dim(w) == dim(h)))
  dA <- w
  for (i in 1:nrow(dA)) {
    dA[i, ] <- calcdA_vec(w[i, ], h[i, ])
  }
  dA
}


#' Calculate partial cross-section area from width and height vectors (time series)
#' @param w vector of widths
#' @param h vector of heights(FROM MARK)
calcdA_vec <- function(w, h) {
  words <- order(w)
  warr <- w[words]
  harr <- h[words]
  delh <- c(0, diff(harr))
  delA <- cumsum(warr * delh)
  dA <- 1:length(w)
  dA[words] <- delA
  dA
}

#Calculate slope
#' Calculate slope based on height and along-river distance
#' @param xvec vector of x (along-stream) distances, measured from
#' upstream-most cross-section
#' @param hmat Matrix (space-down, time-across) of stream heights above
#'arbitrary datum.(FROM MARK)
calcslope <- function(xvec, hmat) {
  dH <- apply(hmat, 2, function(x) c(NA, -diff(x)))
  dX_vec <- c(NA, diff(xvec))
  dX <- matrix(dX_vec, ncol = ncol(hmat), nrow = nrow(hmat),
               byrow = FALSE)
  out <- dH / dX
}


#Vector of distances between pt coordinates
calc_xvec <- function(pt_coords_sp, cl){
  coords = cl@lines[[1]]@Lines[[1]]@coords
  csum = cumsum(pointDistance(coords[1:(nrow(coords)-1),], coords[2:nrow(coords),], lonlat = FALSE))
  dist_mat = pointDistance(pt_coords_sp, data.frame(cl@lines[[1]]@Lines[[1]]@coords))
  xvec = csum[apply(dist_mat, 1, FUN = which.min)]
  return(xvec)
}

PAD_bamdata <- function(WSE_all, WSE_Q, Q, bamdata, xvec, rivname){
  #Calculate dA
  calcdA_mat <- function(w, h) {
    stopifnot(all(dim(w) == dim(h)))
    dA <- w
    for (i in 1:nrow(dA)) {
      dA[i, ] <- calcdA_vec(w[i, ], h[i, ])
    }
    dA
  }
  calcdA_vec <- function(w, h) {
    words <- order(w)
    warr <- w[words]
    harr <- h[words]
    delh <- c(0, diff(harr))
    delA <- cumsum(warr * delh)
    dA <- 1:length(w)
    dA[words] <- delA
    dA
  }
  
  #Calculate slope
  calcslope <- function(xvec, hmat) {
    dH <- apply(hmat, 2, function(x) c(NA, -diff(x)))
    dX_vec <- c(NA, diff(xvec))
    dX <- matrix(dX_vec, ncol = ncol(hmat), nrow = nrow(hmat),
                 byrow = FALSE)
    out <- dH / dX
  }

  WSE_all$date = as.Date(WSE_all$new_time)

  
  WSE_all = aggregate(.~date, data = WSE_all, FUN = mean)
  height = t(WSE_all[, 4:(ncol(WSE_all))])
  width = matrix(bamdata$Wobs[1,1], nrow = (ncol(WSE_all)-3), ncol = nrow(WSE_all))
  dA = calcdA_mat(width, height)
  slope = calcslope(xvec = xvec, hmat = height)
  slope = rbind(colMeans(slope, na.rm = TRUE), slope)
  slope = slope[c(1, 3:nrow(slope)),]
  slope[slope<=0] = min(slope[slope>0], na.rm = TRUE)
  slope[is.na(slope)] = mean(slope, na.rm = TRUE)
  data = bam_data(w = width, s = slope, dA = dA, Qhat = exp(bamdata$logQ_hat))
  return(data)
}

```

## Athabasca

You can also embed plots, for example:

```{r Athabasca, echo=FALSE}
library(dplyr)
library(bamr)
library(rgdal)
library(sp)
library(raster)

#load WSE
Athabasca_WSE <- read.csv("../input/PAD/Raw/Athabasca/WSE/Athabasca_WSE_PPP_corr.csv")
Athabasca_WSE <- Athabasca_WSE %>%
  mutate(day = as.Date(new_time, format="%Y-%m-%d"))
Athabasca_WSE_daily <- aggregate(. ~day, data = Athabasca_WSE, mean, na.rm = TRUE)[,c(4:ncol(Athabasca_WSE))]

#load Q
PAD_2018_ADCP <- read.csv("../input/PAD/Raw/PAD_2018_ADCP.csv")
Athabasca_qobs_df <- PAD_2018_ADCP[startsWith(as.character(PAD_2018_ADCP$Location),"ATH"),]
Athabasca_corr_Q <- Athabasca_qobs_df[Athabasca_qobs_df$Q>600,]

Athabasca_corr_Q <- Athabasca_corr_Q %>%
  mutate(day = as.Date(new_date, format="%Y-%m-%d"))


#load cl and PT coords
wd = getwd()
setwd("../input/PAD/Centerline")
Athabasca_cl <-readOGR(dsn = ".", layer = "Athabasca_cl_UTM")
setwd(wd)

Athabasca_PT_coords <- read.csv("../input/PAD/PT_coords/Athabasca_PT_coords.csv")
Athabasca_PT_coords_sp <-SpatialPoints(Athabasca_PT_coords[,4:5], 
                                       proj4string = crs('+proj=utm +zone=12 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0' ))

#calculate the distance between pts
Athabasca_xvec <- calc_xvec(Athabasca_PT_coords_sp, Athabasca_cl)

#find overlapping ADCP and PT times
Athabasca_closest_time <- vector(length = length(Athabasca_corr_Q$new_date))
for(i in 1:length(Athabasca_corr_Q$new_date)){
  Athabasca_closest_time[i] = which.min(abs(as.POSIXct(Athabasca_WSE$new_time, tz = "MST") - 
                                              as.POSIXct(Athabasca_corr_Q$new_date[i], tz = "MST")))
}

Athabasca_WSE_corrQ <- Athabasca_WSE[c(Athabasca_closest_time[order(Athabasca_closest_time)]),c(3:7)]

#Calculate slope
Athabasca_slope <- calcslope(sort(Athabasca_xvec), hmat = t(Athabasca_WSE_corrQ[, order(Athabasca_xvec)]))
Athabasca_slope[1,] <- colMeans(Athabasca_slope, na.rm = TRUE)

#Get width from ADCP data
Athabasca_width = matrix(rep(Athabasca_corr_Q$Width, nrow(Athabasca_slope)), nrow = nrow(Athabasca_slope), byrow= TRUE)

#Calculate dA
Athabasca_dA = calcdA_mat(w = Athabasca_width, h = t(Athabasca_WSE_corrQ))

#Split into two reaches
Athabasca_data = bam_data(w = Athabasca_width, s = Athabasca_slope, dA = Athabasca_dA, Qhat = Athabasca_corr_Q$Q)

Athabasca_data$dAobs[,1] = rowMeans(Athabasca_data$dAobs)
Athabasca_R1_data = bam_data(w = Athabasca_data$Wobs[c(1,2),43:46], Athabasca_data$Sobs[c(1,2),43:46],
                              dA = Athabasca_data$dAobs[c(1,2),43:46], 
                              Qhat = Athabasca_corr_Q[43:46,"Q"])

Athabasca_R2_data = bam_data(w = Athabasca_data$Wobs[c(3:5),1:42], Athabasca_data$Sobs[c(3:5),1:42],
                               dA = Athabasca_data$dAobs[c(3:5),1:42], 
                               Qhat = Athabasca_corr_Q[1:42,"Q"])

Athabasca_R1_corr_Q = Athabasca_corr_Q[43:46,]
Athabasca_R1_WSE = Athabasca_WSE[c(1:4)]

Athabasca_R2_corr_Q = Athabasca_corr_Q[1:42,]
Athabasca_R2_WSE = Athabasca_WSE[c(1,2,5,6,7)]

#Full time series
Athabasca_R1_full_data = PAD_bamdata(WSE_all = Athabasca_WSE[c(1:4)], WSE_Q = Athabasca_WSE_corrQ[43:46, 1:2], 
                                       bamdata = Athabasca_R1_data,
                                       xvec = Athabasca_xvec[1:2], rivname = "Athabasca R1", Q = Athabasca_corr_Q[43:46,])
Athabasca_R2_full_data = PAD_bamdata(WSE_all = Athabasca_WSE[c(1:2,5,6,7)], WSE_Q = Athabasca_WSE_corrQ[1:42, 3:5], 
                                            bamdata = Athabasca_R2_data,
                                            xvec = Athabasca_xvec[3:5], rivname = "Athabasca R2", Q = Athabasca_corr_Q[1:42,])
#Save
saveRDS(Athabasca_R1_data, file = "../input/PAD/BAMdata/Athabasca_R1_data.rds")
saveRDS(Athabasca_R1_full_data, file = "../input/PAD/BAMdata/Athabasca_R1_full_data.rds")
saveRDS(Athabasca_R2_data, file = "../input/PAD/BAMdata/Athabasca_R2_data.rds")
saveRDS(Athabasca_R2_data, file = "../input/PAD/BAMdata/Athabasca_R2_full_data.rds")

saveRDS(Athabasca_R1_corr_Q, file = "../input/PAD/BAMdata/Athabasca_R1_corr_Q.rds")
saveRDS(Athabasca_R1_WSE, file = "../input/PAD/BAMdata/Athabasca_R1_WSE.rds")

saveRDS(Athabasca_R2_corr_Q, file = "../input/PAD/BAMdata/Athabasca_R2_corr_Q.rds")
saveRDS(Athabasca_R2_WSE, file = "../input/PAD/BAMdata/Athabasca_R2_WSE.rds")

bam_plot(Athabasca_R1_data)
bam_plot(Athabasca_R2_data)

```
## Coupe

You can also embed plots, for example:

```{r Coupe, echo=FALSE}
library(dplyr)
library(bamr)
library(rgdal)
library(sp)
library(raster)

#load WSE
Coupe_WSE <- read.csv("../input/PAD/Raw/Coupe/WSE/Coupe_WSE_PPP_corr.csv")
Coupe_WSE <- Coupe_WSE %>%
  mutate(day = as.Date(new_time, format="%Y-%m-%d"))

#load Q
PAD_2018_ADCP <- read.csv("../input/PAD/Raw/PAD_2018_ADCP.csv")
Coupe_qobs_df <- PAD_2018_ADCP[startsWith(as.character(PAD_2018_ADCP$Location),"CP"),]
Coupe_corr_Q <- Coupe_qobs_df[Coupe_qobs_df$Q>100,]

Coupe_corr_Q <- Coupe_corr_Q %>%
  mutate(day = as.Date(new_date, format="%Y-%m-%d"))

#load cl and PT coords
wd = getwd()
setwd("../input/PAD/Centerline")
Coupe_cl <-readOGR(dsn = ".", layer = "Coupe_CL_UTM")
setwd(wd)

Coupe_PT_coords <- read.csv("../input/PAD/PT_coords/Coupe_PT_coords.csv")
Coupe_PT_coords_sp <-SpatialPoints(Coupe_PT_coords[,4:5], 
                                       proj4string = crs('+proj=utm +zone=12 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0' ))
#calculate the distance between pts
Coupe_xvec <- calc_xvec(Coupe_PT_coords_sp, Coupe_cl)

#find overlapping ADCP and PT times
Coupe_closest_time <- vector(length = length(Coupe_corr_Q$new_date))
for(i in 1:length(Coupe_corr_Q$new_date)){
  Coupe_closest_time[i] = which.min(abs(as.POSIXct(Coupe_WSE$new_time, tz = "MST") - 
                                              as.POSIXct(Coupe_corr_Q$new_date[i], tz = "MST")))
}

Coupe_WSE_corrQ <- Coupe_WSE[c(Coupe_closest_time[order(Coupe_closest_time)]),c(3:7)]

#Calculate slope
Coupe_slope <- -1*calcslope(sort(Coupe_xvec[1:5]), hmat = t(Coupe_WSE_corrQ[, order(Coupe_xvec[1:5])]))
Coupe_slope[1,] <- colMeans(Coupe_slope, na.rm = TRUE)

#Get width from ADCP data
Coupe_width = matrix(rep(Coupe_corr_Q$Width, nrow(Coupe_slope)), nrow = nrow(Coupe_slope), byrow= TRUE)

#Calculate dA
Coupe_dA = calcdA_mat(w = Coupe_width, h = t(Coupe_WSE_corrQ))

#Save as bamdata
Coupe_data = bam_data(w = Coupe_width, s = Coupe_slope, dA = Coupe_dA, Qhat = Coupe_corr_Q$Q)

Coupe_full_data = PAD_bamdata(WSE_all = Coupe_WSE[,c(1:7,9)], WSE_Q = Coupe_WSE_corrQ, bamdata = Coupe_data,
                                   xvec = rev(Coupe_xvec), rivname = "Coupe", Q = Coupe_corr_Q)


saveRDS(Coupe_data, file = "../input/PAD/BAMdata/Coupe_data.rds")
saveRDS(Coupe_full_data, file = "../input/PAD/BAMdata/Coupe_full_data.rds")
saveRDS(Coupe_corr_Q, file = "../input/PAD/BAMdata/Coupe_corr_Q.rds")
saveRDS(Coupe_WSE[,c(1:7,9)], file = "../input/PAD/BAMdata/Coupe_WSE.rds")

bamr::bam_plot(Coupe_bamdata)
```


## Fletcher

```{r Fletcher, echo=FALSE}
library(dplyr)
library(bamr)
library(rgdal)
library(sp)
library(raster)

#load WSE
Fletcher_WSE <- read.csv("../input/PAD/Raw/Fletcher/WSE/Fletcher_WSE_PPP_corr.csv")
Fletcher_WSE <- Fletcher_WSE %>%
  mutate(day = as.Date(new_time, format="%Y-%m-%d"))
Fletcher_WSE_daily <- aggregate(. ~day, data = Fletcher_WSE, mean, na.rm = TRUE)[,c(4:ncol(Fletcher_WSE))]

#load Q
PAD_2018_ADCP <- read.csv("../input/PAD/Raw/PAD_2018_ADCP.csv")
Fletcher_qobs_df <- PAD_2018_ADCP[startsWith(as.character(PAD_2018_ADCP$Location),"FL"),]
Fletcher_corr_Q <- Fletcher_qobs_df[Fletcher_qobs_df$Q>100,]

Fletcher_corr_Q <- Fletcher_corr_Q %>%
  mutate(day = as.Date(new_date, format="%Y-%m-%d"))

#load cl and PT coords
wd = getwd()
setwd("../input/PAD/Centerline")
Fletcher_cl <-readOGR(dsn = ".", layer = "Fletcher_CL_UTM")
setwd(wd)

Fletcher_PT_coords <- read.csv("../input/PAD/PT_coords/Fletcher_PT_coords.csv")
Fletcher_PT_coords_sp <-SpatialPoints(Fletcher_PT_coords[,4:5], 
                                       proj4string = crs('+proj=utm +zone=12 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0' ))
#calculate the distance between pts
Fletcher_xvec <- calc_xvec(Fletcher_PT_coords_sp, Fletcher_cl)

#find overlapping ADCP and PT times
Fletcher_closest_time <- vector(length = length(Fletcher_corr_Q$new_date))
for(i in 1:length(Fletcher_corr_Q$new_date)){
  Fletcher_closest_time[i] = which.min(abs(as.POSIXct(Fletcher_WSE$new_time, tz = "MST") - 
                                              as.POSIXct(Fletcher_corr_Q$new_date[i], tz = "MST")))
}

Fletcher_WSE_corrQ <- Fletcher_WSE[c(Fletcher_closest_time[order(Fletcher_closest_time)]),c(3,4,6,7)]

#Calculate slope
Fletcher_slope <- calcslope(sort(Fletcher_xvec[c(3:5)]), hmat = t(Fletcher_WSE_corrQ[, order(Fletcher_xvec[c(3:5)])]))
Fletcher_slope[1,] <- colMeans(Fletcher_slope, na.rm = TRUE)

#Get width from ADCP data
Fletcher_width = matrix(rep(Fletcher_corr_Q$Width, nrow(Fletcher_slope)), nrow = nrow(Fletcher_slope), byrow= TRUE)

#Calculate dA
Fletcher_dA = calcdA_mat(w = Fletcher_width, h = t(Fletcher_WSE_corrQ[, order(Fletcher_xvec[c(3:5)])]))

#Save as bamdata
Fletcher_data = bam_data(w = Fletcher_width, s = Fletcher_slope, dA = Fletcher_dA, Qhat = Fletcher_corr_Q$Q)

Fletcher_full_data = PAD_bamdata(WSE_all = Fletcher_WSE[c(1:4,6,8)], WSE_Q = Fletcher_WSE_corrQ[,c(1:3)], bamdata = Fletcher_data,
                                      xvec = Fletcher_xvec[c(3:5)], rivname = "Fletcher", Q = Fletcher_corr_Q)

saveRDS(Fletcher_data, file = "../input/PAD/BAMdata/Fletcher_data.rds")
saveRDS(Fletcher_full_data, file = "../input/PAD/BAMdata/Fletcher_full_data.rds")
saveRDS(Fletcher_corr_Q, file = "../input/PAD/BAMdata/Fletcher_corr_Q.rds")
saveRDS(Fletcher_WSE[c(1:4,6,8)], file = "../input/PAD/BAMdata/Fletcher_WSE.rds")

bamr::bam_plot(Fletcher_data)
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
`

## Mamawi

```{r Mamawi, echo=FALSE}
library(dplyr)
library(bamr)
library(rgdal)
library(sp)
library(raster)

#load WSE
Mamawi_WSE <- read.csv("../input/PAD/Raw/Mamawi/WSE/Mamawi_WSE_PPP_corr.csv")
Mamawi_WSE <- Mamawi_WSE %>%
  mutate(day = as.Date(new_time, format="%Y-%m-%d"))

#load Q
PAD_2018_ADCP <- read.csv("../input/PAD/Raw/PAD_2018_ADCP.csv")
Mamawi_qobs_df <- PAD_2018_ADCP[startsWith(as.character(PAD_2018_ADCP$Location),"M"),]
Mamawi_corr_Q <- Mamawi_qobs_df

Mamawi_corr_Q <- Mamawi_corr_Q %>%
  mutate(day = as.Date(new_date, format="%Y-%m-%d"))

#load cl and PT coords
wd = getwd()
setwd("../input/PAD/Centerline")
Mamawi_cl <-readOGR(dsn = ".", layer = "Mamawi_CL_UTM")
setwd(wd)

Mamawi_PT_coords <- read.csv("../input/PAD/PT_coords/Mamawi_PT_coords.csv")
Mamawi_PT_coords_sp <-SpatialPoints(Mamawi_PT_coords[,4:5], 
                                       proj4string = crs('+proj=utm +zone=12 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0' ))
#calculate the distance between pts
Mamawi_xvec <- calc_xvec(Mamawi_PT_coords_sp, Mamawi_cl)

#find overlapping ADCP and PT times
Mamawi_closest_time <- vector(length = length(Mamawi_corr_Q$new_date))
for(i in 1:length(Mamawi_corr_Q$new_date)){
  Mamawi_closest_time[i] = which.min(abs(as.POSIXct(Mamawi_WSE$new_time, tz = "MST") - 
                                              as.POSIXct(Mamawi_corr_Q$new_date[i], tz = "MST")))
}

Mamawi_WSE_corrQ <- Mamawi_WSE[c(Mamawi_closest_time[order(Mamawi_closest_time)]),c(3,4,6,8)]

#Calculate slope
Mamawi_slope <- -1*calcslope(sort(Mamawi_xvec[c(1,2,4,6)]), hmat = t(Mamawi_WSE_corrQ[, order(Mamawi_xvec[c(1,2,4,6)])]))
Mamawi_slope[1,] <- colMeans(Mamawi_slope, na.rm = TRUE)

#Get width from ADCP data
Mamawi_width = matrix(rep(Mamawi_corr_Q$Width, nrow(Mamawi_slope)), nrow = nrow(Mamawi_slope), byrow= TRUE)

#Calculate dA
Mamawi_dA = calcdA_mat(w = Mamawi_width, h = t(Mamawi_WSE_corrQ))

#Save as bamdata
Mamawi_data = bam_data(w = Mamawi_width, s = Mamawi_slope, dA = Mamawi_dA, Qhat = Mamawi_corr_Q$Q)

Mamawi_full_data = PAD_bamdata(WSE_all = Mamawi_WSE[,c(1:4,6,8,9)], WSE_Q = Mamawi_WSE_corrQ, bamdata = Mamawi_data,
                                      xvec = rev(Mamawi_xvec[c(1,2,4,6)]), rivname = "Mamawi", Q = Mamawi_corr_Q)

saveRDS(Mamawi_data, file = "../input/PAD/BAMdata/Mamawi_data.rds")
saveRDS(Mamawi_full_data, file = "../input/PAD/BAMdata/Mamawi_full_data.rds")
saveRDS(Mamawi_corr_Q, file = "../input/PAD/BAMdata/Mamawi_corr_Q.rds")
saveRDS(Mamawi_WSE[,c(1:4,6,8,9)], file = "../input/PAD/BAMdata/Mamawi_WSE.rds")

bamr::bam_plot(Mamawi_data)
```

## QF

```{r QF, echo=FALSE}
library(dplyr)
library(bamr)
library(rgdal)
library(sp)
library(raster)

#load WSE
QF_WSE <- read.csv("../input/PAD/Raw/QF/WSE/QF_WSE_PPP_corr.csv")
QF_WSE <- QF_WSE %>%
  mutate(day = as.Date(new_time, format="%Y-%m-%d"))

#load Q
PAD_2018_ADCP <- read.csv("../input/PAD/Raw/PAD_2018_ADCP.csv")
QF_qobs_df <- PAD_2018_ADCP[startsWith(as.character(PAD_2018_ADCP$Location),"QF"),]
QF_corr_Q <- QF_qobs_df[QF_qobs_df$Q> 300,]

QF_corr_Q <- QF_corr_Q %>%
  mutate(day = as.Date(new_date, format="%Y-%m-%d"))

#load cl and PT coords
wd = getwd()
setwd("../input/PAD/Centerline")
QF_cl <-readOGR(dsn = ".", layer = "QF_CL_UTM")
setwd(wd)

QF_PT_coords <- read.csv("../input/PAD/PT_coords/QF_PT_coords.csv")
QF_PT_coords_sp <-SpatialPoints(QF_PT_coords[,4:5], 
                                       proj4string = crs('+proj=utm +zone=12 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0' ))
#calculate the distance between pts
QF_xvec <- calc_xvec(QF_PT_coords_sp, QF_cl)

#find overlapping ADCP and PT times
QF_closest_time <- vector(length = length(QF_corr_Q$new_date))
for(i in 1:length(QF_corr_Q$new_date)){
  QF_closest_time[i] = which.min(abs(as.POSIXct(QF_WSE$new_time, tz = "MST") - 
                                              as.POSIXct(QF_corr_Q$new_date[i], tz = "MST")))
}

QF_WSE_corrQ <- QF_WSE[c(QF_closest_time[order(QF_closest_time)]),c(3:8)]

#Calculate slope
QF_slope <- -1*calcslope(sort(QF_xvec[c(1:6)]), hmat = t(QF_WSE_corrQ[, order(QF_xvec[c(1:6)])]))
QF_slope[1,] <- colMeans(QF_slope, na.rm = TRUE)

#Get width from ADCP data
QF_width = matrix(rep(QF_corr_Q$Width, nrow(QF_slope)), nrow = nrow(QF_slope), byrow= TRUE)

#Calculate dA
QF_dA = calcdA_mat(w = QF_width, h = t(QF_WSE_corrQ))

#Save as bamdata
QF_data = bam_data(w = QF_width, s = QF_slope, dA = QF_dA, Qhat = QF_corr_Q$Q)

QF_full_data = PAD_bamdata(WSE_all = QF_WSE[,c(1:8,10)], WSE_Q = QF_WSE_corrQ, bamdata = QF_data,
                                      xvec = QF_xvec, rivname = "QF", Q = QF_corr_Q)

saveRDS(QF_data, file = "../input/PAD/BAMdata/QF_data.rds")
saveRDS(QF_full_data, file = "../input/PAD/BAMdata/QF_full_data.rds")
saveRDS(QF_corr_Q, file = "../input/PAD/BAMdata/QF_corr_Q.rds")
saveRDS(QF_WSE[,c(1:8,10)], file = "../input/PAD/BAMdata/QF_WSE.rds")

bamr::bam_plot(QF_data)
```



## Rochers

```{r Rochers, echo=FALSE}
library(dplyr)
library(bamr)
library(rgdal)
library(sp)
library(raster)

#load WSE
Rochers_WSE <- read.csv("../input/PAD/Raw/Rochers/WSE/Rochers_WSE_PPP_corr.csv")
Rochers_WSE <- Rochers_WSE %>%
  mutate(day = as.Date(new_time, format="%Y-%m-%d"))

#load Q
PAD_2018_ADCP <- read.csv("../input/PAD/Raw/PAD_2018_ADCP.csv")
Rochers_qobs_df <- PAD_2018_ADCP[startsWith(as.character(PAD_2018_ADCP$Location),"R"),]
Rochers_corr_Q <- Rochers_qobs_df[Rochers_qobs_df$Q > 1400,]

Rochers_corr_Q <- Rochers_corr_Q %>%
  mutate(day = as.Date(new_date, format="%Y-%m-%d"))

#load cl and PT coords
wd = getwd()
setwd("../input/PAD/Centerline")
Rochers_cl <-readOGR(dsn = ".", layer = "Rochers_CL_UTM")
setwd(wd)

Rochers_PT_coords <- read.csv("../input/PAD/PT_coords/Rochers_PT_coords.csv")
Rochers_PT_coords_sp <-SpatialPoints(Rochers_PT_coords[,4:5], 
                                       proj4string = crs('+proj=utm +zone=12 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0' ))
#calculate the distance between pts
Rochers_xvec <- calc_xvec(Rochers_PT_coords_sp, Rochers_cl)

#find overlapping ADCP and PT times
Rochers_closest_time <- vector(length = length(Rochers_corr_Q$new_date))
for(i in 1:length(Rochers_corr_Q$new_date)){
  Rochers_closest_time[i] = which.min(abs(as.POSIXct(Rochers_WSE$new_time, tz = "MST") - 
                                              as.POSIXct(Rochers_corr_Q$new_date[i], tz = "MST")))
}

Rochers_WSE_corrQ <- Rochers_WSE[c(Rochers_closest_time[order(Rochers_closest_time)]),c(3:7)]

#Calculate slope
Rochers_slope <- calcslope(rev(sort(Rochers_xvec[c(1:3,5,6)])), hmat = t(Rochers_WSE_corrQ[, order(Rochers_xvec[c(1:3,5,6)])]))
Rochers_slope[1,] <- colMeans(Rochers_slope, na.rm = TRUE)

#Get width from ADCP data
Rochers_width = matrix(rep(Rochers_corr_Q$Width, nrow(Rochers_slope)), nrow = nrow(Rochers_slope), byrow= TRUE)

#Calculate dA
Rochers_dA = calcdA_mat(w = Rochers_width, h = t(Rochers_WSE_corrQ))

#Save as bamdata
Rochers_data = bam_data(w = Rochers_width, s = Rochers_slope, dA = Rochers_dA, Qhat = Rochers_corr_Q$Q)

Rochers_R1_data = bam_data(w = Rochers_data$Wobs[c(1:3),15:32], Rochers_data$Sobs[c(1:3),15:32],
                              dA = Rochers_data$dAobs[c(1:3),15:32], 
                             Qhat = Rochers_corr_Q[15:32,"Q"])

Rochers_R2_data = bam_data(w = Rochers_data$Wobs[c(4:5),c(1:14, 33:45)], Rochers_data$Sobs[c(4:5),c(1:14, 33:45)],
                              dA = Rochers_data$dAobs[c(4:5),c(1:14, 33:45)], 
                             Qhat = Rochers_corr_Q[c(1:14, 33:45),"Q"])

Rochers_R1_full_data= PAD_bamdata(WSE_all = Rochers_WSE[,1:5], WSE_Q = Rochers_WSE_corrQ[15:32, 1:3], 
                                          bamdata = Rochers_R1_data,
                                          xvec = Rochers_xvec[1:3], rivname = "Rochers", Q = Rochers_corr_Q[15:32,])
Rochers_R2_full_data = PAD_bamdata(WSE_all = Rochers_WSE[,c(1,2,6,7)], WSE_Q = Rochers_WSE_corrQ[c(1:14, 33:45), 4:5], 
                                          bamdata = Rochers_R2_data,
                                          xvec = Rochers_xvec[5:4], rivname = "Rochers", Q = Rochers_corr_Q[c(1:14, 33:45),])

saveRDS(Rochers_R1_data, file = "../input/PAD/BAMdata/Rochers_R1_data.rds")
saveRDS(Rochers_R2_data, file = "../input/PAD/BAMdata/Rochers_R2_data.rds")

saveRDS(Rochers_R1_full_data, file = "../input/PAD/BAMdata/Rochers_R1_full_data.rds")
saveRDS(Rochers_R2_full_data, file = "../input/PAD/BAMdata/Rochers_R2_full_data.rds")

saveRDS(Rochers_corr_Q[15:32,], file = "../input/PAD/BAMdata/Rochers_R1_corr_Q.rds")
saveRDS(Rochers_WSE[,1:5], file = "../input/PAD/BAMdata/Rochers_R1_WSE.rds")

saveRDS(Rochers_corr_Q[c(1:14, 33:45),], file = "../input/PAD/BAMdata/Rochers_R2_corr_Q.rds")
saveRDS(Rochers_WSE[,c(1,2,6,7)], file = "../input/PAD/BAMdata/Rochers_R2_WSE.rds")

bamr::bam_plot(Rochers_R1_data)
bamr::bam_plot(Rochers_R2_data)

```


## Embarras

You can also embed plots, for example:

```{r Embarras, echo=FALSE}
library(dplyr)
library(bamr)
library(rgdal)
library(sp)
library(raster)

#load WSE
Embarras_WSE <- read.csv("../input/PAD/Raw/Embarras/WSE/Embarras_WSE_PPP_corr.csv")
Embarras_WSE <- Embarras_WSE %>%
  mutate(day = as.Date(new_time, format="%Y-%m-%d"))
Embarras_WSE_daily <- aggregate(. ~day, data = Embarras_WSE, mean, na.rm = TRUE)[,c(4:ncol(Embarras_WSE))]

#load Q
PAD_2019_ADCP <- read.csv("../input/PAD/Raw/PAD_2019_ADCP.csv")
Embarras_qobs_df <- PAD_2019_ADCP[startsWith(as.character(PAD_2019_ADCP$Location),"EM"),]
Embarras_qobs_df <- Embarras_qobs_df %>%
  mutate(day = as.Date(new_date, format="%Y-%m-%d"))
Embarras_corr_Q <- Embarras_qobs_df[Embarras_qobs_df$Q > 100 & Embarras_qobs_df$Q < 200, ]

Embarras_corr_Q <- Embarras_corr_Q %>%
  mutate(day = as.Date(new_date, format="%Y-%m-%d"))


#load cl and PT coords
wd = getwd()
setwd("../input/PAD/Centerline")
Embarras_cl <-readOGR(dsn = ".", layer = "Embarras_CL_UTM")
setwd(wd)

Embarras_PT_coords <- read.csv("../input/PAD/PT_coords/Embarras_PT_coords.csv")
Embarras_PT_coords_sp <-SpatialPoints(Embarras_PT_coords[,4:5], 
                                       proj4string = crs('+proj=utm +zone=12 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0' ))

#calculate the distance between pts
Embarras_xvec <- calc_xvec(Embarras_PT_coords_sp, Embarras_cl)

#find overlapping ADCP and PT times
Embarras_closest_time <- vector(length = length(Embarras_corr_Q$new_date))
for(i in 1:length(Embarras_corr_Q$new_date)){
  Embarras_closest_time[i] = which.min(abs(as.POSIXct(Embarras_WSE$new_time, tz = "MST") - 
                                              as.POSIXct(Embarras_corr_Q$new_date[i], tz = "MST")))
}

Embarras_WSE_corrQ <- Embarras_WSE[c(Embarras_closest_time[order(Embarras_closest_time)]),c(3:6)]

#Calculate slope
Embarras_slope <- abs(calcslope(sort(Embarras_xvec[c(1:2,4,5)]), hmat = t(Embarras_WSE_corrQ)))
Embarras_slope[1,] <- colMeans(Embarras_slope, na.rm = TRUE)

#Get width from ADCP data
Embarras_width = matrix(rep(as.numeric(Embarras_corr_Q$Width), nrow(Embarras_slope)), nrow = nrow(Embarras_slope), byrow= TRUE)

#Calculate dA
Embarras_dA = calcdA_mat(w = Embarras_width, h = t(Embarras_WSE_corrQ))

#Split into two reaches
Embarras_data = bam_data(w = Embarras_width, s = Embarras_slope, dA = Embarras_dA, Qhat = Embarras_corr_Q$Q)

Embarras_data = bam_data(w = Embarras_data$Wobs[c(1,2),c(1:5,7,8,15:17,36,37)], 
                              Embarras_data$Sobs[c(1,2),c(1:5,7,8,15:17,36,37)],
                               dA = Embarras_data$dAobs[c(1,2),c(1:5,7,8,15:17,36,37)], 
                              Qhat = Embarras_corr_Q[c(1:5,7,8,15:17,36,37),"Q"])

#Full time series
Embarras_full_data = PAD_bamdata(WSE_all = Embarras_WSE[,c(1:4)], WSE_Q = Embarras_WSE_corrQ[c(1:5,7,8,15:17,36,37), 1:2], 
                                           bamdata = Embarras_data,
                                           xvec = Embarras_xvec[1:2], rivname = "Embarras", 
                                           Q = Embarras_corr_Q[c(1:5,7,8,15:17,36,37),])
#Save
saveRDS(Embarras_data, file = "../input/PAD/BAMdata/Embarras_data.rds")
saveRDS(Embarras_full_data, file = "../input/PAD/BAMdata/Embarras_full_data.rds")
saveRDS(Embarras_corr_Q, file = "../input/PAD/BAMdata/Embarras_corr_Q.rds")
saveRDS(Embarras_WSE[,c(1:4)], file = "../input/PAD/BAMdata/Embarras_WSE.rds")

bam_plot(Embarras_data)


```

## Limon

You can also embed plots, for example:

```{r Limon, echo=FALSE}
library(dplyr)
library(bamr)
library(rgdal)
library(sp)
library(raster)

#load WSE
Limon_WSE <- read.csv("../input/PAD/Raw/Limon/WSE/Limon_WSE_PPP_corr.csv")
Limon_WSE <- Limon_WSE %>%
  mutate(day = as.Date(new_time, format="%Y-%m-%d"))
Limon_WSE_daily <- aggregate(. ~day, data = Limon_WSE, mean, na.rm = TRUE)[,c(4:ncol(Limon_WSE))]

#load Q
PAD_2019_ADCP <- read.csv("../input/PAD/Raw/PAD_2019_ADCP.csv")
Limon_qobs_df <- PAD_2019_ADCP[startsWith(as.character(PAD_2019_ADCP$Location),"NR"),]
Limon_qobs_df <- Limon_qobs_df %>%
  mutate(day = as.Date(new_date, format="%Y-%m-%d"))
Limon_corr_Q <- Limon_qobs_df[Limon_qobs_df$Q > 30 & Limon_qobs_df$Q < 50,]

Limon_corr_Q <- Limon_corr_Q %>%
  mutate(day = as.Date(new_date, format="%Y-%m-%d"))


#load cl and PT coords
wd = getwd()
setwd("../input/PAD/Centerline")
Limon_cl <-readOGR(dsn = ".", layer = "Limon_CL_UTM")
setwd(wd)

Limon_PT_coords <- read.csv("../input/PAD/PT_coords/Limon_PT_coords.csv")
Limon_PT_coords_sp <-SpatialPoints(Limon_PT_coords[,4:5], 
                                       proj4string = crs('+proj=utm +zone=12 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0' ))

#calculate the distance between pts
Limon_xvec <- calc_xvec(Limon_PT_coords_sp, Limon_cl)

#find overlapping ADCP and PT times
Limon_closest_time <- vector(length = length(Limon_corr_Q$new_date))
for(i in 1:length(Limon_corr_Q$new_date)){
  Limon_closest_time[i] = which.min(abs(as.POSIXct(Limon_WSE$new_time, tz = "MST") - 
                                              as.POSIXct(Limon_corr_Q$new_date[i], tz = "MST")))
}

Limon_WSE_corrQ <- Limon_WSE[c(Limon_closest_time[order(Limon_closest_time)]),c(3:6)]

#Calculate slope
Limon_slope <- abs(calcslope(Limon_xvec[c(1,2,3,5)], hmat = t(Limon_WSE_corrQ)))
Limon_slope[1,] <- colMeans(Limon_slope, na.rm = TRUE)

#Get width from ADCP data
Limon_width = matrix(rep(as.numeric(Limon_corr_Q$Width), nrow(Limon_slope)), nrow = nrow(Limon_slope), byrow= TRUE)

#Calculate dA
Limon_dA = calcdA_mat(w = Limon_width, h = t(Limon_WSE_corrQ))

#Split into two reaches
Limon_data = bam_data(w = Limon_width, s = Limon_slope, dA = Limon_dA, Qhat = Limon_corr_Q$Q)

#Full time series
Limon_full_data = PAD_bamdata(WSE_all = Limon_WSE, WSE_Q = Limon_WSE_corrQ, bamdata = Limon_data,
                                   xvec = Limon_xvec, rivname = "Limon", Q = Limon_corr_Q)
#Save
saveRDS(Limon_data, file = "../input/PAD/BAMdata/Limon_data.rds")
saveRDS(Limon_full_data, file = "../input/PAD/BAMdata/Limon_full_data.rds")
saveRDS(Limon_corr_Q, file = "../input/PAD/BAMdata/Limon_corr_Q.rds")
saveRDS(Limon_WSE, file = "../input/PAD/BAMdata/Limon_WSE.rds")

bam_plot(Limon_data)


```


## Richardson

You can also embed plots, for example:

```{r Richardson, echo=FALSE}
library(dplyr)
library(bamr)
library(rgdal)
library(sp)
library(raster)

#load WSE
Richardson_WSE <- read.csv("../input/PAD/Raw/Richardson/WSE/Richardson_WSE_PPP_corr.csv")
Richardson_WSE <- Richardson_WSE %>%
  mutate(day = as.Date(new_time, format="%Y-%m-%d"))
Richardson_WSE_daily <- aggregate(. ~day, data = Richardson_WSE, mean, na.rm = TRUE)[,c(4:ncol(Richardson_WSE))]

#load Q
PAD_2019_ADCP <- read.csv("../input/PAD/Raw/PAD_2019_ADCP.csv")
Richardson_qobs_df <- PAD_2019_ADCP[startsWith(as.character(PAD_2019_ADCP$Location),"R"),]
Richardson_qobs_df <- Richardson_qobs_df %>%
  mutate(day = as.Date(new_date, format="%Y-%m-%d"))
Richardson_corr_Q <- Richardson_qobs_df[Richardson_qobs_df$Q < 25,]

Richardson_corr_Q <- Richardson_corr_Q %>%
  mutate(day = as.Date(new_date, format="%Y-%m-%d"))


#load cl and PT coords
wd = getwd()
setwd("../input/PAD/Centerline")
Richardson_cl <-readOGR(dsn = ".", layer = "Richardson_CL_UTM")
setwd(wd)

Richardson_PT_coords <- read.csv("../input/PAD/PT_coords/Richardson_PT_coords.csv")
Richardson_PT_coords_sp <-SpatialPoints(Richardson_PT_coords[,4:5], 
                                       proj4string = crs('+proj=utm +zone=12 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0' ))

#calculate the distance between pts
Richardson_xvec <- calc_xvec(Richardson_PT_coords_sp, Richardson_cl)

#find overlapping ADCP and PT times
Richardson_closest_time <- vector(length = length(Richardson_corr_Q$new_date))
for(i in 1:length(Richardson_corr_Q$new_date)){
  Richardson_closest_time[i] = which.min(abs(as.POSIXct(Richardson_WSE$new_time, tz = "MST") - 
                                              as.POSIXct(Richardson_corr_Q$new_date[i], tz = "MST")))
}

Richardson_WSE_corrQ <- Richardson_WSE[c(Richardson_closest_time[order(Richardson_closest_time)]),c(3:7)]

#Calculate slope
Richardson_slope <- abs(calcslope(Richardson_xvec, hmat = t(Richardson_WSE_corrQ)))
Richardson_slope[1,] <- colMeans(Richardson_slope, na.rm = TRUE)

#Get width from ADCP data
Richardson_width = matrix(rep(as.numeric(Richardson_corr_Q$Width), nrow(Richardson_slope)), nrow = nrow(Richardson_slope), byrow= TRUE)

#Calculate dA
Richardson_dA = calcdA_mat(w = Richardson_width, h = t(Richardson_WSE_corrQ))

#Split into two reaches
Richardson_data = bam_data(w = Richardson_width, s = Richardson_slope, dA = Richardson_dA, Qhat = Richardson_corr_Q$Q)

#Full time series
Richardson_full_data = PAD_bamdata(WSE_all = Richardson_WSE, WSE_Q = Richardson_WSE_corrQ, bamdata = Richardson_data,
                                        xvec = Richardson_xvec, rivname = "Richardson", Q = Richardson_corr_Q)
#Save
saveRDS(Richardson_data, file = "../input/PAD/BAMdata/Richardson_data.rds")
saveRDS(Richardson_full_data, file = "../input/PAD/BAMdata/Richardson_full_data.rds")
saveRDS(Richardson_corr_Q, file = "../input/PAD/BAMdata/Richardson_corr_Q.rds")
saveRDS(Richardson_WSE, file = "../input/PAD/BAMdata/Richardson_WSE.rds")

bam_plot(Richardson_data)


```



